\documentclass[journal]{IEEEtran}

% \usepackage{algorithm}

% \usepackage[noend]{algpseudocode}
%\usepackage[ruled, linesnumbered, vlined, commentsnumbered]{algorithm2e}
\usepackage{graphicx,subcaption} % figure related
\usepackage{amsfonts,amssymb,amsmath,amsthm,amsopn}	% math related
\usepackage{hhline,booktabs,colortbl,multirow,tabularx,diagbox,threeparttable} % table related
\usepackage[listings,skins,breakable]{tcolorbox}
\usepackage[ruled, vlined, linesnumbered, commentsnumbered]{algorithm2e}

\usepackage{enumerate}
\usepackage{authblk}
\usepackage{footnote}
\usepackage{hyperref}
\usepackage{prettyref}
\usepackage{cite}
\usepackage{setspace}
\usepackage{color}
\usepackage{xcolor}  % Required for custom colors

\usepackage{relsize}

\usepackage{pgfplots}
\pgfplotsset{compat=1.12}
\usepackage{tikz}

\tcbset{colback=white, arc=0mm, outer arc=0pt}

%\usepackage[section]{placeins}

\def\hlinew#1{%
  \noalign{\ifnum0=`}\fi\hrule \@height #1 \futurelet
   \reserved@a\@xhline}
\makeatother

\definecolor{mycyan}{gray}{.7}
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{property}{Property}

\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

\let\oldnl\nl% Store \nl in \oldnl
\newcommand{\noln}{\renewcommand{\nl}{\let\nl\oldnl}}

% \newcommand\CONDITION[2]%
%   {\begin{tabular}[t]{@{}l@{}l@{}}
%      #1&#2
%    \end{tabular}%
%   }
% \algdef{SE}[WHILE]{While}{EndWhile}[1]%
%   {\algorithmicwhile\ \CONDITION{#1}{\ \algorithmicdo}}%
%   {\algorithmicend\ \algorithmicwhile}
% \algdef{SE}[FOR]{For}{EndFor}[1]%
%   {\algorithmicfor\ \CONDITION{#1}{\ \algorithmicdo}}%
%   {\algorithmicend\ \algorithmicfor}
% \algdef{S}[FOR]{ForAll}[1]%
%   {\algorithmicforall\ \CONDITION{#1}{\ \algorithmicdo}}
% \algdef{SE}[REPEAT]{Repeat}{Until}{\algorithmicrepeat}[1]%
%   {\algorithmicuntil\ \CONDITION{#1}{}}
% \algdef{SE}[IF]{If}{EndIf}[1]%
%   {\algorithmicif\ \CONDITION{#1}{\ \algorithmicthen}}%
%   {\algorithmicend\ \algorithmicif}%
% \algdef{C}[IF]{IF}{ElsIf}[1]%
%   {\algorithmicelse\ \algorithmicif\ \CONDITION{#1}{\ \algorithmicthen}}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\newcommand\notealf[1]{\mbox{}\marginpar{\footnotesize\raggedright\hspace{0pt}\color{blue}\emph{#1}}}
\newcommand{\pref}{\prettyref}

\newrefformat{fig}{Fig.~\ref{#1}}
\newrefformat{tab}{Table~\ref{#1}}
\newrefformat{sec}{Section~\ref{#1}}
\newrefformat{app}{Appendix~\ref{#1}}
\newrefformat{alg}{Algorithm~\ref{#1}}
\newrefformat{property}{Property~\ref{#1}}
\newrefformat{theorem}{Theorem~\ref{#1}}
\newrefformat{lemma}{Lemma~\ref{#1}}
\newrefformat{corollary}{Corollary~\ref{#1}}
\newrefformat{proposition}{Proposition~\ref{#1}}
\newrefformat{def}{Definition~\ref{#1}}
\newrefformat{eq}{equation~(\ref{#1})}

\captionsetup{compatibility=false}

\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}

\newcommand{\abs}[1]{\left\lvert #1 \right\rvert}

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

\setlength{\belowcaptionskip}{-1em}

\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}

\begin{document}
%
%\title{A Formal Model for Multi-objective Optimisation of Network Function Virtualisation Placement}
\title{Multi-Objective Virtual Network Function Placement: A Formal Model and Effective Algorithms}
%
%\titlerunning{A Formal Model for Multi-objective Optimisation of NFV Placement}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
	Joseph Billingsley,~\IEEEmembership{Student Member,~IEEE},
	Ke Li,~\IEEEmembership{Member,~IEEE},
	Wang Miao,
	Geyong Min,
	Nektarios Georgalas
	\thanks{J. Billingsley, K. Li, W. Miao and G. Min are with the Department of Computer Science, University of Exeter, North Park Road, Exeter, EX4 4QF, UK (e-mail: \{j.billingsley, k.li, wang.miao, g.min\}@exeter.ac.uk)}
	\thanks{N. Georgalas is with the Research and Innovation, British Telecom, Martlesham, UK (e-mail: nektarios.georgalas@bt.com)}
}

\maketitle

% TODO:
% Remove figures, remove text, fix citations, remove white space, remove words to fit on one line

\begin{abstract}  
Data centers are critical to the commercial and social activities of modern society but are also major electricity consumers. To minimize their environmental impact, it is imperative to make data centers more energy efficient while maintaining a high quality of service (QoS). Bearing this consideration in mind, we develop an analytical model using queueing theory for evaluating the QoS of a data center. Furthermore, based on this model, we develop a domain-specific evolutionary optimization framework featuring a tailored solution representation and a constraint-aware initialization operator for finding the optimal placement of virtual network functions in a data center that optimizes multiple conflicting objectives with regard to energy consumption and QoS. In particular, our framework is applicable to any existing evolutionary multi-objective optimization algorithm in a plug-in manner. Extensive experiments validate the efficiency and accuracy of our QoS model as well as the effectiveness of our tailored algorithms for virtual network function placement problems at various scales.

%In this work, we consider how a key data center component, virtual network functions can be placed in the data center to optimize the conflicting objectives of energy consumption and quality of service. This papers aims to show that multi-objective EAs can address the issues faced by existing algorithms and are suitable candidates for virtual network function placement problems (VNFPPs) in industry. This work makes two major contributions. First, we propose a new solution representation for the VNFPP that guarantees the feasibility of solutions and a novel genetic operator for initialization. Second, we propose a fast, accurate model of the data center that captures the complexities of the VNFPP better than existing models. 

%We then show how these two innovations can be integrated into three state of the art multi-objective evolutionary algorithms and evaluate the performance of the resulting algorithms. Our results show that our proposed algorithm can solve far larger problems than existing exact methods and also greatly outperforms scalable heuristic approaches to the VNFPP. Whilst evolutionary algorithms have so far been underappreciated in the VNFPP literature, our research shows they have the potential to revolutionize the field. 
%Existing approaches typically rely on exact methods that cannot scale to large problems or heuristic methods with limited applications. Meanwhile, meta-heuristic methods such as evolutionary algorithms (EAs) have received little attention. 
\end{abstract}

\begin{IEEEkeywords}
	Virtual network function, queueing theory, QoS modeling, evolutionary multi-objective optimization.
\end{IEEEkeywords}

\input{introduction}

\input{related}

\input{problem_formulation}

\input{system_model}

\input{optimisation}

\input{experiments}

\input{conclusions}

\section*{Acknowledgment}
K. Li was supported by UKRI Future Leaders Fellowship (Grant No. MR/S017062/1) and Amazon Research Awards. J. Billingsley was supported by EPSRC Industrial CASE and British Telecom (Grant No. 16000177).

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bibliography}

\end{document}
