% !TeX root = main.tex

\noindent\textbf{--\ Response to Associate Editor}\\

\textsf{Authors are suggested to think which area they aim to contribute, a network communication area or an evolutionary computation area, revise this manuscript and choose a journal in the best area. If they aim to contribute in an EC area, our transactions is a good choice but emphasize their contribution to the EC research; if not, consider the suggestion of the second referee.}\\
\textcolor{blue}{\textbf{\textit{Reply}: We thank the associate editor for their comments. It is our goal with this work to introduce an important problem to the EC community, one which we believe that EC is well positioned to solve. By way of illustration, we developed new models and operators to demonstrate how EC concepts can improve the state of the art in this area. In the updated manuscript, we have made several modifications to emphasize our contributions to EC and \textit{vice versa}, EC research to the VNFPP. In particular, we would like to bring the attention of the associated editors to the following changes that are particularly pertinent:
        \begin{enumerate}
            \item To make clear the particular relevance of this research to Transactions on Cybernetics, we have updated many of the references to refer to relevant papers previously published in this journal.
            \item We have also extended the experiments section to have a greater focus on the evolutionary algorithm at the core of the paper. In particular we have conducted further experiments to analyse different solution representations in detail (see response to reviewer 1, points 3 and 5), and of different evolutionary frameworks (see response to review 3, point 2).
        \end{enumerate}}}

\textsf{This manuscript was submitted in this May, and authors' paper with a similar title was presented at EMO2021 held in this March. Please answer to the question from the third referee; it may be better to provide the EMO2021 paper together with authors' answer to three referees for fair check if authors submit their revision.
}\\
\textcolor{blue}{\textbf{\textit{Reply}: We have prepared a detailed response to this question in answer to the comments of the third referee.}}

\clearpage
